---
title: "Open Search Exploration"
author: "Scott Brenstuhl"
date: "August 10, 2016"
output: 
    md_document:
        variant: markdown_github
---
        
```{r libraries, alert=FALSE, message = FALSE, echo = FALSE}
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
```


```{r}
queries <- read_csv("data/all_queries.csv")

# Check what these errors are from
problems(queries)

# We should remove these weird rows
# Did every sheet that got combined create one?
View(tail(queries))

```

## Understanding the Data
This data is coming from Google analytics "Site Search" functionality, which is
hooked up to the SF Open Data portal's search page. 

A lot of the useful information about this can be found at: 
https://developers.google.com/analytics/devguides/reporting/core/dimsmets



#### ga.searchKeyword(Search Terms)

These are the words and keywords that have been entered into the search form at
https://data.sfgov.org/



#### ga.searchStartPage(Search Page) 

Page on site where the user enters terms for a web search


#### ga.searchAfterDestinationPage(Search Destination Page)

The page that users visited after performing an internal search on the site.



#### ga.searchUniques(Total Unique Searches)

The total number of times your site search was used. This excludes multiple 
searches on the same keyword during the same session.



#### ga.avgSearchResultViews(Results Pageviews / Search)

The average number of times people viewed a page as a result of a search.



#### ga.avgSearchDepth(Average Search Depth)

The average number of pages people viewed after performing a search.



#### ga.percentSearchRefinements(Search Refinements)

The percentage of the number of times a refinement (i.e., transition) occurs 
between internal keywords search within a session.



#### ga.searchDuration(Time after Search)

The session duration when the site's internal search feature is used.



#### ga.searchExitRate(Search Exits)

The percentage of searches that resulted in an immediate exit from the property.

- What is the difference between searchAfterDestinationPage == (exit) and 
searchExitRate == 100?

```{r}
filter(queries,ga.searchAfterDestinationPage == '(exit)')
```

